% !TeX root = ../main_socg.tex

We have extended the Topological Coverage Criterion to the setting of Topological Scalar Field Analysis.
By defining the boundary in terms of a sublevel set of a scalar field we provide an interpretation of the TCC that applies more naturally to data coverage.
We then showed how the assumptions and machinery of the TCC can be used to approximate the persistent homology of the scalar field relative to a static sublevel set.
This relative persistent homology is shown to be related to a truncation of that of the scalar field as whole, and therefore provides a way to approximate a part of its persistence diagram in the presence of un-verified data.

There are a number of unanswered questions and directions for future work.
From the theoretical perspective, our understanding of duality limited us in providing a more elegant extension of the TCC.
A better understanding of when and how duality can be applied would allow us to give a more rigorous statement of our assumptions.
Moreover, as duality plays a central role in the TCC it is natural to investigate its role in the analysis of scalar fields.
This would not only allow us to apply duality to persistent homology~\cite{desilva11duality}, but also allow us to provide a rigorous comparison between the relative approach and the persistent homology of the superlevel set filtration and explore connections with Extended Persistence~\cite{cohen09extending}.

From a computational perspective, we interested in exploring how to recover the full diagram as discussed in Section~\ref{sec:experiments}.
Our statements in terms of sublevel sets can be generalized to disjoint unions of sub and superlevel sets, where coverage is confirmed in an \emph{interlevel} set.
This, along with a better understanding of the relationship between sub and superlevel sets could lead to an iterative approach in which the persistent homology of a scalar field is constructed as data becomes available.
We are also interested in finding efficient ways to compute the image persistent (relative) homology that vary in both scalar and scale.

The problem of relaxing our assumptions on the boundary can be approached from both a theoretical and computational perspective.
Ways to avoid the isomorphism we require could be investigated in theory, and the interaction of relative persistent homology and the Persistent Nerve Lemma may be used tighten our assumptions.
We would also like to conduct a more rigorous investigation on the effect of these assumptions in practice.
